On Secure Delegation of SampBQP with a Classical Client

### 2020-01-21 preliminaries.tex
Add first draft definition of CPA for protocols

\begin{dfn}
	Let $(\bbP, \bbV)(x)$ be an interactive protocol with the verifier's initial input being $x$. Then it is IND-CPA secure if, for any $x_1, x_2$, any polynomial time adversary $\cA$,
	$$\abs{\Pr\left[TODO\right]}-TODO$$

\end{dfn}

>>>>

\begin{dfn}
	Let $(\bbP, \bbV)(x)$ be an interactive protocol with the verifier's initial input being $x$. Then it is IND-CPA secure if any polynomial time adversary $\cA$ can't win \protoref{protoIndCPA} with probability better than $\frac{1}{2}+\negl(\lambda)$ \Ethan{Check if it's actually lambda}
\end{dfn}

\floatname{algorithm}{Protocol}
\begin{algorithm}
	\caption{ $\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoQPIP1}
	\begin{algorithmic}[1]
		\State \Ethan{Do we need some kinda generalization of Keygen here...?}
		\State $\cA$ picks strings $c_1$ and $c_2$ and sends them to the challenger
		\State The challenger picks $c_b$ at random where $b\in\set{0,1}$
		\State The challenger runs the protocol with the adversary, acting as the verifier with input $c_b$
		\State $\cA$ attempts to guess $b$
	\end{algorithmic}
\end{algorithm}
\floatname{algorithm}{Algorithm}
